# Integrated Load Monitoring Proof of Concept

This is a Bayesian Proof-of-Concept for Injury Risk Reduction and Performance Optimisation in Elite Football

Claude Opus 4.6 was used to aid routine coding tasks. 

```{r, echo = FALSE, message = FALSE, warning=FALSE} 
# Loading required plots 
require(brms)        # Bayesian regression models via Stan
require(ggplot2)     # Visualisation
require(dplyr)       # Data wrangling
require(tidyr)       # Reshaping
require(tidybayes)   # Tidy extraction of posterior draws
require(patchwork)   # Combining plots

set.seed(2026)  # Reproducibility
```

## Part 1 - Generating and Visualing synthetic data for training and matches

Simulate 25 players in different positions across 38 match weeks. Each player has daily training data (MD-5 to MD-1) plus match-day data.

This mirrors the microcycle structure described in Morgans et al. (2025):
- MD-5: compensation/recovery
- MD-4: strength & power, explosive actions
- MD-3: tactical, high-intensity, position-specific
- MD-2: low-intensity technical-tactical ("underloaded")
- MD-1: neural stimulation, set-plays

External load: total distance (m/min), HSR distance (m/min), sprint distance (m/min), accelerations (n/min)

Internal load: sRPE (RPE × session duration), wellness score (1–10)

```{r}


# Squad structure 
positions <- c(
  rep("CB", 5), rep("FB", 5), rep("CM", 5),
  rep("AM", 5), rep("CF", 5)
)
n_players <- length(positions)
player_ids <- paste0("P", sprintf("%02d", 1:n_players))
player_names <- paste0(positions, "_", rep(1:5, 5))

player_df <- data.frame(
  player_id = player_ids,
  player_name = player_names,
  position = positions,
  stringsAsFactors = FALSE
)

# True positional baselines for TRAINING session external load (m/min)
pos_td_train  <- c(CB = 95, FB = 105, CM = 110, AM = 105, CF = 98)   # total distance 
pos_hsr_train <- c(CB = 1.5, FB = 2.5, CM = 2.0, AM = 2.8, CF = 2.2) # HSR m/min

# True positional baselines for MATCH external load (m/min)
# Higher than training, calibrated to match-play literature
pos_hsr_match <- c(CB = 3.0, FB = 5.5, CM = 4.5, AM = 6.0, CF = 5.0) # HSR m/min in matches

# Player-specific random effects (individual variation around position mean)
player_re_hsr <- rnorm(n_players, 0, 0.5)  # SD ~0.5 m/min
player_re_wellness <- rnorm(n_players, 0, 0.5) # baseline wellness variation

```

```{r}
# Generate Weekly data

n_weeks <- 38
all_data <- list()

for (w in 1:n_weeks) {
  for (p in 1:n_players) {
    pos <- player_df$position[p]

    # --- Training days (5 sessions: MD-5 to MD-1) ---
    # Session intensity follows the published microcycle pattern
    # MD-4 and MD-3 are the highest-load days
    session_intensity <- c(0.6, 0.95, 0.85, 0.5, 0.3)  # MD-5 to MD-1
    session_duration  <- c(60, 75, 80, 60, 45)           # minutes

    for (d in 1:5) {
      # External load: HSR distance per minute
      hsr <- (pos_hsr_train[pos] + player_re_hsr[p]) *
        session_intensity[d] +
        rnorm(1, 0, 0.3)
      hsr <- max(hsr, 0)

      # Total distance (correlated with HSR but with positional variation)
      td <- (pos_td_train[pos] + rnorm(1, 0, 5)) *
        session_intensity[d] * (session_duration[d] / 60)

      # Sprint distance per minute (subset of HSR, lower values)
      sprint <- hsr * runif(1, 0.15, 0.35)

      # Accelerations per minute
      accel <- 1.5 * session_intensity[d] + rnorm(1, 0, 0.3)

      # Internal load: RPE (1-10) and session duration → sRPE
      rpe <- round(pmin(pmax(
        session_intensity[d] * 7 + rnorm(1, 0, 1), 1), 10), 1)
      srpe <- rpe * session_duration[d]

      # Wellness score (1-10): influenced by cumulative load and individual
      # Higher load earlier in week → lower wellness later
      base_wellness <- 7 + player_re_wellness[p] -
        0.003 * (w * 5 + d) * session_intensity[d] +  # seasonal fatigue
        rnorm(1, 0, 0.5)
      wellness <- round(pmin(pmax(base_wellness, 1), 10), 1)

      all_data[[length(all_data) + 1]] <- data.frame(
        player_id = player_ids[p],
        position = pos,
        week = w,
        day_type = paste0("MD-", 6 - d),
        is_match = FALSE,
        session_duration = session_duration[d],
        hsr_per_min = round(hsr, 2),
        td_metres = round(td, 0),
        sprint_per_min = round(sprint, 3),
        accel_per_min = round(accel, 2),
        rpe = rpe,
        srpe = round(srpe, 0),
        wellness = wellness,
        match_hsr = NA_real_,
        stringsAsFactors = FALSE
      )
    }

    # --- Match day ---
    # Not all players play every week (rotation, injury, tactical choice)
    plays_match <- runif(1) < 0.7  # ~70% availability per week
    match_mins <- if (plays_match) sample(c(90, 90, 90, 75, 60), 1) else 0

    if (plays_match) {
      match_hsr <- pos_hsr_match[pos] + player_re_hsr[p] + rnorm(1, 0, 0.6)
      match_hsr <- max(match_hsr, 0)

      all_data[[length(all_data) + 1]] <- data.frame(
        player_id = player_ids[p],
        position = pos,
        week = w,
        day_type = "MD",
        is_match = TRUE,
        session_duration = match_mins,
        hsr_per_min = round(match_hsr, 2),
        td_metres = round(match_mins * runif(1, 105, 125), 0),
        sprint_per_min = round(match_hsr * runif(1, 0.2, 0.4), 3),
        accel_per_min = round(2.0 + rnorm(1, 0, 0.4), 2),
        rpe = round(pmin(pmax(7.5 + rnorm(1, 0, 1), 4), 10), 1),
        srpe = NA_real_,
        wellness = NA_real_,
        match_hsr = round(match_hsr, 2),
        stringsAsFactors = FALSE
      )
    }
  }
}

dat <- bind_rows(all_data)
cat(sprintf("Simulated %d daily records for %d players across %d weeks\n",
            nrow(dat), n_players, n_weeks))


```


```{r}
# Training Data Summarised

train_summary <- dat %>%
  filter(!is_match) %>%
  group_by(position) %>%
  summarise(
    n_sessions    = n(),
    n_players     = n_distinct(player_id),
    hsr_mean      = round(mean(hsr_per_min, na.rm = TRUE), 2),
    hsr_sd        = round(sd(hsr_per_min, na.rm = TRUE), 2),
    sprint_mean   = round(mean(sprint_per_min, na.rm = TRUE), 3),
    accel_mean    = round(mean(accel_per_min, na.rm = TRUE), 2),
    srpe_mean     = round(mean(srpe, na.rm = TRUE), 0),
    wellness_mean = round(mean(wellness, na.rm = TRUE), 1),
    .groups = "drop"
  ) %>%
  arrange(desc(hsr_mean))

print(as.data.frame(train_summary))


```


```{r}
# Match data summarised

match_summary <- dat %>%
  filter(is_match) %>%
  group_by(position) %>%
  summarise(
    n_matches     = n(),
    n_players     = n_distinct(player_id),
    match_hsr_mean = round(mean(match_hsr, na.rm = TRUE), 2),
    match_hsr_sd   = round(sd(match_hsr, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  arrange(desc(match_hsr_mean))

print(as.data.frame(match_summary))

```

## Part 2 — Derive workload features

Key features for modelling:
- ACWR (Acute:Chronic Workload Ratio) — rolling 7-day / 28-day external load (HSR-based), computed per player

- Weekly sRPE load (sum of daily sRPE across the training week)

- Weekly mean wellness score

- External-internal mismatch: when external load is high but internal response is disproportionately elevated -> risk signal

```{r}
# Aggregate to weekly level per player
weekly <- dat %>%
  filter(!is_match) %>%
  group_by(player_id, position, week) %>%
  summarise(
    weekly_hsr_load = sum(hsr_per_min * session_duration, na.rm = TRUE),
    weekly_td_load  = sum(td_metres, na.rm = TRUE),
    weekly_srpe     = sum(srpe, na.rm = TRUE),
    mean_wellness   = mean(wellness, na.rm = TRUE),
    .groups = "drop"
  )

# Compute rolling acute (1-week) and chronic (4-week exponentially weighted)
# loads per player, then ACWR
weekly <- weekly %>%
  arrange(player_id, week) %>%
  group_by(player_id) %>%
  mutate(
    acute_load  = weekly_hsr_load,
    chronic_load = zoo::rollmean(weekly_hsr_load, k = 4, fill = NA,
                                  align = "right"),
    acwr = ifelse(!is.na(chronic_load) & chronic_load > 0,
                  acute_load / chronic_load, NA_real_),
    # Standardise features for modelling
    z_acwr = as.numeric(scale(acwr)),
    z_srpe = as.numeric(scale(weekly_srpe)),
    z_wellness = as.numeric(scale(mean_wellness))
  ) %>%
  ungroup()

# External-internal mismatch: residual of sRPE ~ external load regression
# High positive residual = internal response is elevated relative to
# external stimulus → possible fatigue/illness signal
fit_mismatch <- lm(weekly_srpe ~ weekly_hsr_load, data = weekly)
weekly$ei_mismatch <- as.numeric(scale(residuals(fit_mismatch)))

# Add match-day HSR (the performance outcome) from match records
match_perf <- dat %>%
  filter(is_match) %>%
  select(player_id, week, match_hsr)

weekly <- weekly %>%
  left_join(match_perf, by = c("player_id", "week"))

```

```{r}
# Base injury rate ~5-8% per player-week (realistic for EPL squads)

player_vulnerability <- setNames(rnorm(n_players, 0, 0.3), player_ids)

weekly <- weekly %>%
  filter(!is.na(acwr)) %>%
  mutate(
    # Log-odds of injury
    logit_injury = -3.0 +                                    # base rate ~4.5%
      0.8 * z_acwr +                                         # ACWR effect
      -0.4 * z_wellness +                                    # low wellness → higher risk
      0.3 * ei_mismatch +                                    # mismatch signal
      player_vulnerability[player_id],                        # individual frailty
    p_injury = plogis(logit_injury),
    injured = rbinom(n(), 1, p_injury)
  )

cat(sprintf("Injury rate: %.1f%% of player-weeks\n",
            mean(weekly$injured, na.rm = TRUE) * 100))
cat(sprintf("Modelling dataset: %d player-weeks with complete data\n",
            sum(complete.cases(weekly[, c("acwr", "weekly_srpe",
                                          "mean_wellness", "injured")]))))
```


## Part 3 — Model A: Bayesian Hierarchical Logistic Regression (Injury Risk)

This section fits a Bayesian hierarchical logistic regression to model weekly injury probability as a function of each player's current load state. The model specification is:

$$
\text{injured}_i \sim \text{Bernoulli}(p_i)
$$

$$
\text{logit}(p_i) = \beta_0 + \beta_1 \cdot \text{ACWR}_i + \beta_2 \cdot \text{Wellness}_i + \beta_3 \cdot \text{EI\_Mismatch}_i + u_{\text{player}} + v_{\text{position}}
$$

where $u_{\text{player}} \sim \mathcal{N}(0, \sigma^2_u)$ and $v_{\text{position}} \sim \mathcal{N}(0, \sigma^2_v)$ are random intercepts capturing individual vulnerability and positional baseline risk respectively.


```{r fit-injury-model, results="hide", message=FALSE, warning=FALSE}

model_injury <- brm(
  injured ~ z_acwr + z_wellness + ei_mismatch + (1 | player_id) + (1 | position),
  data = weekly,
  family = bernoulli(link = "logit"),
  prior = c(
    prior(normal(0, 1), class = "b"),           # weakly informative on fixed effects
    prior(normal(-3, 1), class = "Intercept"),   # centre on low base rate
    prior(exponential(2), class = "sd")          # half-normal on group SDs
  ),
  chains = 4,
  iter = 5000,
  warmup = 1000,
  seed = 42,
  cores = 4, 
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  silent = 2
)

# cat("Model A fitted successfully.\n")
# summary(model_injury)
```


```{r fit-performance-model, results="hide", message=FALSE, warning=FALSE}
perf_data <- weekly %>%
  filter(!is.na(match_hsr))

cat(sprintf("\n--- Fitting Model B: Match Performance (n = %d match observations) ---\n",
            nrow(perf_data)))
cat("This will take 2-4 minutes...\n")

model_performance <- brm(
  match_hsr ~ z_acwr + z_srpe + z_wellness + (1 | player_id) + (1 | position),
  data = perf_data,
  family = gaussian(),
  prior = c(
    prior(normal(0, 1), class = "b"),
    prior(normal(5, 2), class = "Intercept"),    # centre on ~5 m/min mean
    prior(exponential(2), class = "sd"),
    prior(exponential(1), class = "sigma")
  ),
  chains = 4,
  iter = 5000,
  warmup = 1000,
  seed = 42,
  silent = 2
)

cat("Model B fitted successfully.\n")
summary(model_performance)
```

## Part 5 — Decision Dashboard 

This is the deliverable for a Tuesday team meeting:

- Panel 1: Player-level injury risk posteriors for the upcoming week
- Panel 2: Expected match-day HSR performance posteriors
- Panel 3: Risk-performance trade-off scatter (the decision quadrant)
- Panel 4: ACWR "sweet spot" — how injury risk and performance vary across the ACWR spectrum

```{r}
# Generate predictions for the most recent week 

current_week <- weekly %>%
  group_by(player_id) %>%
  slice_max(week, n = 1) %>%
  ungroup()

# Posterior predicted injury probabilities
injury_preds <- posterior_epred(model_injury, newdata = current_week)

injury_summary <- data.frame(
  player_id = current_week$player_id,
  position = current_week$position,
  acwr = round(current_week$acwr, 2),
  wellness = round(current_week$mean_wellness, 1),
  p_injury_mean = round(colMeans(injury_preds), 3),
  p_injury_lower = round(apply(injury_preds, 2, quantile, 0.05), 3),
  p_injury_upper = round(apply(injury_preds, 2, quantile, 0.95), 3)
)

# Posterior predicted match performance (for players who might play)
perf_preds <- posterior_epred(model_performance, newdata = current_week,
                               allow_new_levels = TRUE)

perf_summary <- data.frame(
  player_id = current_week$player_id,
  position = current_week$position,
  hsr_mean = round(colMeans(perf_preds), 2),
  hsr_lower = round(apply(perf_preds, 2, quantile, 0.1), 2),
  hsr_upper = round(apply(perf_preds, 2, quantile, 0.9), 2)
)

# Merge for the decision dashboard
dashboard <- injury_summary %>%
  left_join(perf_summary %>% select(player_id, hsr_mean, hsr_lower, hsr_upper),
            by = "player_id")

```

```{r}
# --- 5b. PANEL 1: Injury Risk Forest Plot ------------------------------------
p1 <- dashboard %>%
  mutate(player_label = paste0(player_id, " (", position, ")")) %>%
  arrange(p_injury_mean) %>%
  mutate(player_label = factor(player_label, levels = player_label)) %>%
  ggplot(aes(x = p_injury_mean, y = player_label, colour = position)) +
  geom_point(size = 2.5) +
  geom_errorbarh(aes(xmin = p_injury_lower, xmax = p_injury_upper),
                 height = 0.3, linewidth = 0.6) +
  geom_vline(xintercept = 0.10, linetype = "dashed", colour = "red",
             alpha = 0.6) +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, NA)) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Posterior Injury Risk — This Week",
    subtitle = "90% credible intervals | Red line = 10% risk threshold",
    x = "P(Injury This Week)",
    y = NULL,
    colour = "Position"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.position = "bottom"
  )

print(p1)
```

```{r}
p2 <- dashboard %>%
  mutate(player_label = paste0(player_id, " (", position, ")")) %>%
  arrange(hsr_mean) %>%
  mutate(player_label = factor(player_label, levels = player_label)) %>%
  ggplot(aes(x = hsr_mean, y = player_label, colour = position)) +
  geom_point(size = 2.5) +
  geom_errorbarh(aes(xmin = hsr_lower, xmax = hsr_upper),
                 height = 0.3, linewidth = 0.6) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Posterior Expected Match HSR (m/min)",
    subtitle = "80% credible intervals | Higher = more high-speed output expected",
    x = "Expected HSR (m/min)",
    y = NULL,
    colour = "Position"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.position = "bottom"
  )

print(p2)
```

```{r}

p3 <- dashboard %>%
  ggplot(aes(x = p_injury_mean, y = hsr_mean, colour = position)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_text(aes(label = player_id), vjust = -0.8, size = 2.5, alpha = 0.7) +
  geom_vline(xintercept = 0.10, linetype = "dashed", colour = "red",
             alpha = 0.5) +
  geom_hline(yintercept = median(dashboard$hsr_mean, na.rm = TRUE),
             linetype = "dashed", colour = "blue", alpha = 0.5) +
  # Quadrant labels — positioned relative to axis limits, not data extremes
  annotate("text", x = 0.02,
           y = max(dashboard$hsr_mean, na.rm = TRUE) * 0.95,
           label = "IDEAL\nHigh performance\nLow risk",
           colour = "darkgreen", size = 3, fontface = "bold", hjust = 0) +
  annotate("text", x = max(dashboard$p_injury_mean, na.rm = TRUE) * 0.85,
           y = max(dashboard$hsr_mean, na.rm = TRUE) * 0.95,
           label = "CAUTION\nHigh performance\nHigh risk",
           colour = "orange3", size = 3, fontface = "bold", hjust = 0) +
  annotate("text", x = 0.02,
           y = min(dashboard$hsr_mean, na.rm = TRUE) * 1.05,
           label = "MONITOR\nLow performance\nLow risk",
           colour = "steelblue", size = 3, fontface = "bold", hjust = 0) +
  annotate("text", x = max(dashboard$p_injury_mean, na.rm = TRUE) * 0.85,
           y = min(dashboard$hsr_mean, na.rm = TRUE) * 1.05,
           label = "RED FLAG\nLow performance\nHigh risk",
           colour = "red3", size = 3, fontface = "bold", hjust = 0) +
  scale_x_continuous(labels = scales::percent_format(),
                     expand = expansion(mult = c(0.05, 0.15))) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.1))) +
  scale_colour_brewer(palette = "Set2") +
  labs(
    title = "Panel 3: Risk–Performance Decision Quadrant",
    subtitle = "Each point = one player's posterior mean this week",
    x = "P(Injury This Week)",
    y = "Expected Match HSR (m/min)",
    colour = "Position"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.position = "bottom"
  )

print(p3)
```

```{r}

acwr_grid <- data.frame(
  z_acwr = seq(-4, 6, length.out = 100),
  z_srpe = 0,
  z_wellness = 0,
  ei_mismatch = 0,
  player_id = NA,
  position = NA
)

# Injury risk across ACWR spectrum (population-level, re_formula = NA)
injury_acwr <- posterior_epred(
  model_injury, newdata = acwr_grid, re_formula = NA,
  allow_new_levels = TRUE
)

# Performance across ACWR spectrum
perf_acwr <- posterior_epred(
  model_performance, newdata = acwr_grid, re_formula = NA,
  allow_new_levels = TRUE
)

# Back-transform ACWR z-scores to raw scale for interpretability
acwr_mean <- mean(weekly$acwr, na.rm = TRUE)
acwr_sd   <- sd(weekly$acwr, na.rm = TRUE)
acwr_grid$acwr_raw <- acwr_grid$z_acwr * acwr_sd + acwr_mean

acwr_plot_data <- data.frame(
  acwr = acwr_grid$acwr_raw,
  injury_mean = colMeans(injury_acwr),
  injury_lower = apply(injury_acwr, 2, quantile, 0.1),
  injury_upper = apply(injury_acwr, 2, quantile, 0.9),
  perf_mean = colMeans(perf_acwr),
  perf_lower = apply(perf_acwr, 2, quantile, 0.1),
  perf_upper = apply(perf_acwr, 2, quantile, 0.9)
)

# Dual-axis plot: injury risk (left axis) and performance (right axis)
# Scale performance to fit on same axis
perf_range <- range(acwr_plot_data$perf_mean)
inj_range  <- range(acwr_plot_data$injury_mean)

p4 <- ggplot(acwr_plot_data, aes(x = acwr)) +
  # Injury risk ribbon and line
  geom_ribbon(aes(ymin = injury_lower, ymax = injury_upper),
              fill = "red", alpha = 0.15) +
  geom_line(aes(y = injury_mean, colour = "Injury Risk"),
            linewidth = 1.2) +
  # Optimal zone annotation
  geom_vline(xintercept = c(0.8, 1.3), linetype = "dotted",
             colour = "grey40", alpha = 0.6) +
  annotate("rect", xmin = 0.8, xmax = 1.3,
           ymin = -Inf, ymax = Inf,
           fill = "green", alpha = 0.05) +
  annotate("text", x = 1.05, y = max(acwr_plot_data$injury_upper) * 0.9,
           label = "Sweet\nSpot",
           colour = "darkgreen", size = 3.5, fontface = "bold") +
  scale_colour_manual(values = c("Injury Risk" = "red")) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "ACWR Sweet Spot: Injury Risk vs Workload",
    subtitle = "Population-level posterior | Green zone: ACWR 0.8–1.3 (Tiernan etpal.)",
    x = "Acute:Chronic Workload Ratio (ACWR)",
    y = "P(Injury)",
    colour = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.position = "bottom"
  )

print(p4)
```



```{r}
# --- What-if scenario: heavy week impact across 4 player profiles ---

# Define 4 contrasting scenarios with narrative context
scenarios_list <- list(
  list(
    player_id = "P01", position = "CB",
    label = "P01 (CB) — High chronic base, consistent starter",
    # Already well-conditioned; heavy week is a smaller relative spike
    z_acwr_heavy = 1.5, z_srpe_heavy = 1.2,
    z_wellness_heavy = -0.5, ei_mismatch_heavy = 0.5
  ),
  list(
    player_id = "P16", position = "AM",
    label = "P16 (AM) — Underloaded, thrown in due to injury crisis",
    # Low chronic base means even moderate acute load creates a huge ACWR spike
    z_acwr_heavy = 3.0, z_srpe_heavy = 2.5,
    z_wellness_heavy = -2.0, ei_mismatch_heavy = 2.0
  ),
  list(
    player_id = "P06", position = "FB",
    label = "P06 (FB) — Mid-season fatigue, congested fixtures",
    # Moderate spike on top of accumulated seasonal load
    z_acwr_heavy = 2.0, z_srpe_heavy = 1.8,
    z_wellness_heavy = -1.5, ei_mismatch_heavy = 1.0
  ),
  list(
    player_id = "P22", position = "CF",
    label = "P22 (CF) — Returning from minor knock, ramping back up",
    # Returning player has low chronic base, moderate acute push
    z_acwr_heavy = 2.5, z_srpe_heavy = 2.0,
    z_wellness_heavy = -1.0, ei_mismatch_heavy = 1.5
  )
)

# Build scenario dataframes
all_scenarios <- list()

for (s in scenarios_list) {
  baseline <- current_week %>% filter(player_id == s$player_id)
  
  heavy <- baseline %>%
    mutate(
      z_acwr = s$z_acwr_heavy,
      z_srpe = s$z_srpe_heavy,
      z_wellness = s$z_wellness_heavy,
      ei_mismatch = s$ei_mismatch_heavy
    )
  
  # Posterior draws for both
  preds <- posterior_epred(model_injury,
                           newdata = bind_rows(baseline, heavy))
  
  draws <- data.frame(
    current = preds[, 1],
    heavy = preds[, 2]
  ) %>%
    pivot_longer(everything(),
                 names_to = "scenario",
                 values_to = "p_injury") %>%
    mutate(
      scenario = ifelse(scenario == "current",
                        "Current Week", "After Heavy Week"),
      scenario = factor(scenario,
                        levels = c("Current Week", "After Heavy Week")),
      player_label = s$label
    )
  
  all_scenarios[[length(all_scenarios) + 1]] <- draws
}

scenario_draws <- bind_rows(all_scenarios)

# Plot: faceted density comparison
ggplot(scenario_draws, aes(x = p_injury, fill = scenario)) +
  geom_density(alpha = 0.55, colour = NA) +
  geom_vline(xintercept = 0.10, linetype = "dashed",
             colour = "red", alpha = 0.6) +
  facet_wrap(~ player_label, ncol = 2, scales = "free_y") +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, 1)) +
  scale_fill_manual(values = c("Current Week" = "steelblue",
                                "After Heavy Week" = "firebrick")) +
  labs(
    title = "What-If Scenarios: How Does a Heavy Week Shift Injury Risk?",
    subtitle = "Posterior density of P(Injury) under current vs. heavy load | Red line = 10% threshold",
    x = "P(Injury This Week)",
    y = "Posterior Density",
    fill = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 13),
    strip.text = element_text(face = "bold", size = 9),
    legend.position = "bottom"
  )
```